PTFO 8-8695: Two Stars, Two Signals, No Planet

### 2020-05-14 paper/ms.tex
fix tex column width

% 0.14 = A1+A2
% 0.06 = A1-A2
% 2A1 = 0.20
% -> A1 = 0.1
% 2A2 = 0.08
% -> A2 = 0.04

@@

% NB: CDIPS-I only made 131 light curves for 25Ori-1, because I wasn't
% aware of the Kounkel+18 member list at the time.
Using the same 149 members in the 25$\,$Ori-1 subgroup, we calculated
the astrometric reduced $\chi^2$ for each member.  We then queried the
CDIPS light curve database at MAST \citep{bouma_cluster_2019} to find
the subset of members that were at least as variable as \ptfo.  We
measured the variability amplitude by taking the difference between
the $95^{\rm th}$ and $5^{\rm th}$ percentiles of the flux
measurements.  This yielded 30 stars of equal or greater variability.
The lower panel of Figure~\ref{fig:gaia} shows the reduced $\chi^2$ as
a function of stellar brightness.  \ptfo\ is in the upper 90$^{\rm
th}$ percentile of stars showing astrometric excesses within the
25$\,$Ori-1 group.  Relative to other M-dwarf group members with
comparable brightnesses and variability characteristics, \ptfo\ still
stands out by virtue of its failure to conform to a single-star
astrometric model. This supports the interpretation that \ptfo\ is a
binary star.

@@

We are not sure what to make of the numerical coincidence.  The ratio
of long to short periods is roughly 10:9.  It is not clear that this
would obviously translate into an observational bias unless, by some
fluke, three season's worth of observations managed to only observe
every ninth dip.  This is of course not the case, and we therefore
leave this curiosity as observation {\it sans} interpretation.
% JNW: This seems like an important clue. I don't have the mental
% energy to ponder it now, but it deserves pondering.
% JNW: Could this mean that both stars are dippers? A change in period
% is degenerate with a change in period, over a short interval, right?
% so maybe one set of dips belongs to one star, the other set to the 2nd star?
% Features with a different period would appear to lie along a line
% of constant slope in this diagram...what would the slope be, in this case,
% if the feature period were P_long?
% LGB: Seems unlikely, because we're seeing a something with constant
% 10.74 hour periodicity, but the phase is offset by 1/9th.
% If both stars were dippers, we would be seeing a 11.98 hour
% periodicity instead.

\subsection{Short Period Modulation Outside of Dips}

Visually, the out-of-dip modulation at the 10.76$\,$hr period
resembles a slightly asymmetric sinusoid (Figure~\ref{fig:phasefold}).
The best model has non-zero amplitudes for both the first and second
harmonics (Table~2).  The third harmonic is formally present with
marginal ($\approx$2$\sigma$) significance.  The first sine and cosine
harmonic both have amplitudes of roughly $0.90\pm0.04\%$.  The second
sine harmonic has amplitude $0.16 \pm 0.04\%$, so is non-zero at a
significance of $\approx$4$\sigma$.  The second cosine harmonic has an
amplitude of $-0.55 \pm 0.03\%$.  In our sign convention, the fact
that it is negative means that this component peaks at phase 0.25 and
0.75, i.e., the quadratures of the orbit.

@@

paper by \citet{koen_2020} that was in press at the
{\it Monthly Notices} before submission of our manuscript.  Our
studies independently reached the same conclusions: the TESS
light curve shows two periodic signals, and the properties of
\ptfo\ are consistent with the emerging class of transient and
persistent flux dip stars.  \citet{koen_2020} reached these
conclusions by modeling the TESS light curve as a truncated sum of
Fourier terms, and concluded that the two signals are most simply
interpreted as coming from two stars.  Our analysis of the Gaia data
provide independent support for the conclusion that \ptfo\ is a
binary. We also note the agreement between the
TESS dip ephemeris and that from \citet{tanimoto_evidence_2020}.

>>>>

@@

Using the same 149 members in the 25$\,$Ori-1 subgroup, we calculated
the astrometric reduced $\chi^2$ for each member.  We then queried the
CDIPS light curve database at MAST \citep{bouma_cluster_2019} to find
the subset of members that were at least as variable as \ptfo.  We
measured the variability amplitude by taking the difference between
the $95^{\rm th}$ and $5^{\rm th}$ percentiles of the flux
measurements.  This yielded 30 stars of equal or greater variability.
The lower panel of Figure~\ref{fig:gaia} shows the reduced $\chi^2$ as
a function of stellar brightness.  \ptfo\ is in the upper 90$^{\rm
th}$ percentile of stars showing astrometric excesses within the
25$\,$Ori-1 group.  Relative to other M-dwarf group members with
comparable brightnesses and variability characteristics, \ptfo\ still
stands out by virtue of its failure to conform to a single-star
astrometric model. This supports the interpretation that \ptfo\ is a
binary star.

@@

We are not sure what to make of the numerical coincidence.  The ratio
of long to short periods is roughly 10:9.  It is not clear that this
would obviously translate into an observational bias unless, by some
fluke, three season's worth of observations managed to only observe
every ninth dip.  This is of course not the case, and we therefore
leave this curiosity as observation {\it sans} interpretation.

\subsection{Short Period Modulation Outside of Dips}
Visually, the out-of-dip modulation at the 10.76$\,$hr period
resembles a slightly asymmetric sinusoid (Figure~\ref{fig:phasefold}).
The best model has non-zero amplitudes for both the first and second
harmonics (Table~2).  The third harmonic is formally present with
marginal ($\approx$2$\sigma$) significance.  The first sine and cosine
harmonic both have amplitudes of roughly $0.90\pm0.04\%$.  The second
sine harmonic has amplitude $0.16 \pm 0.04\%$, so is non-zero at a
significance of $\approx$4$\sigma$.  The second cosine harmonic has an
amplitude of $-0.55 \pm 0.03\%$.  In our sign convention, the fact
that it is negative means that this component peaks at phase 0.25 and
0.75, i.e., the quadratures of the orbit.

@@

paper by \citet{koen_2020} that was in press at the {\it Monthly
Notices} before submission of our manuscript.  Our studies
independently reached the same conclusions: the TESS light curve shows
two periodic signals, and the properties of \ptfo\ are consistent with
the emerging class of transient and persistent flux dip stars.
\citet{koen_2020} reached these conclusions by modeling the TESS light
curve as a truncated sum of Fourier terms, and concluded that the two
signals are most simply interpreted as coming from two stars.  Our
analysis of the Gaia data provide independent support for the
conclusion that \ptfo\ is a binary. We also note the agreement between
the TESS dip ephemeris and that from \citet{tanimoto_evidence_2020}.
